---
title: "Mapping Spatial Networks of Queer Pleasure Within New York City"
runtime: shiny
output: html_document
---
## Introduction to website goals
The map and the companion text-based pages are an extension of my MA paper’s further 
argument that safer sex education during AIDS was negotiated, contested, and 
implemented in public queer spaces by queer actors. It further visually supports 
and provides context for the acts of discrimination and general public health 
debates that impacted queer communities and establishments before and during 
AIDS. It visually argues that the government was both slow to shut down 
bathhouses and backrooms during AIDS and that it continued to use tactics of 
licensing and rezoning to discriminate against the queer community before, 
during, and after the peak of AIDS. The aim of the website is to help
explain queer history in New York City and the layers of medical, governmental,
and social interaction and discrimination with the queer community along with 
helping other people who are interested in tracking queer nightlife in New York
City see changes in the landscape over the course of the end of the 1900s through
visualizing the data I collected at the NYPL archives, the Center archive, and the
NYU archive.

## Introduction to the map content
Below is a map of the five boroughs of New York City's queer bars, clubs, bathhouses, bookstores, cinemas, restaurants, sex stores, backrooms, and cruising locations open between 1970-1986. Some of the establishments were open before 1970 and many of them close after 1986 however those are the bounding years of my study. Below the map will be a link to a Shiny App that will allow further exploration of the locations on this Leaflet map including listing place names and filtering by type of establishment and years of operation. Enjoy!

## The Leaflet Map
```{r}
#| label: set-up
#| include: false
library(osmdata)
library(mapview)
library(tidyverse)
library(sf)
library(tidygeocoder)
library(here)
library(shiny)
library(leaflet)
library(readr)
library(dplyr)

nightlife_geo_sf1 <- st_read(dsn = "data/nightlife_geo_sf1.geojson")


# Brooklyn:
brooklyn_nightlife_geo_sf1 <- st_read(dsn = "data/brooklyn_nightlife_geo_sf1.geojson")

# Bronx:
bronx_nightlife_geo_sf <- st_read(dsn = "data/bronx_nightlife_geo_sf.geojson")

# Queens:
queens_nightlife_geo_sf <- st_read(dsn = "data/queens_nightlife_geo_sf.geojson")

# Staten Island:
staten_nightlife_geo_sf <- st_read(dsn = "data/staten_nightlife_geo_sf.geojson")
```

```{r}
#| fig-align: center

leaflet() %>%
  addTiles() %>%
  setView(-74.00, 40.71, zoom = 11) %>%
  addMarkers(data = nightlife_geo_sf1) %>%  
  addMarkers(data = brooklyn_nightlife_geo_sf1) %>%
  addMarkers(data = bronx_nightlife_geo_sf) %>%
  addMarkers(data = staten_nightlife_geo_sf) %>%
  addMarkers(data = queens_nightlife_geo_sf)
```


## The Shiny Map

 "To access my interactive Shiny application map please use this link!"  
 [Shiny Map](https://kylieedington.shinyapps.io/nightlife/)

 
```

```

